%Two resources useful for abstract writing.
% Guidance of how to write an abstract/summary provided by Nature: https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf %https://writingcenter.gmu.edu/guides/writing-an-abstract
\chapter*{\center \Large  Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Replace all text with your text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The economic condition of traders, customers, and financial institutions has been significantly influenced by the finance sector. With the use of cutting-edge deep learning and machine learning algorithms, artificial intelligence is now rewriting the boundaries of the financial markets. These methods are widely used in financial instrument pricing prediction, portfolio optimization, market trend research, and opportunity identification for investments. Deep learning and machine learning models are used by traders and investors to predict the movements of financial instruments. Investment methods in the stock market are intricate and depend on a thorough analysis of a large quantity of data. The Yahoo-finance dataset displays many firm aspects for stocks, news, quotations, and other items for every potential shift across time. Compared to more conventional methods, machine learning techniques have been studied more and more in the past several years to see if they may enhance market forecasting. 
Using a statistical technique, we conduct a solutional analysis that displays the various company tickers at each instant in time. Based on the needs for the training component, we have taken into consideration three instances of time: one day, one hour, and five minutes, for the dataset to be compared with monthly and yearly wise. 
Depending on the kind of algorithms selected, we label the maximum ticker counts as M, for which M-1 tickers are trained to forecast the final ticker. In order to anticipate stocks or prices for the last tickers, this study will employ Transformer Neural Networks and Arima-ANN hybrids, indicating the DL model. We will then compare the accuracy of these machine learning techniques. 


